---
title: "Feature Selection"
author: "Joy Muli"
date: "11/14/2020"
output:
   md_document:
    variant: markdown_github
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
df_feature <- read.csv(file = 'http://bit.ly/CarreFourDataset')
head(df_feature)
```

# Feature Ranking
# We will use the FSelector Package. This is a package containing functions for selecting attributes from a given dataset. 
```{r}
suppressWarnings(
        suppressMessages(if
                         (!require(FSelector, quietly=TRUE))
                install.packages("FSelector")))
library(FSelector)
```

```{r}
num_cols <- unlist(lapply(df_feature, is.numeric))
num_cols

# Subset numeric columns
data_num <- df_feature[ ,num_cols]
```

# From the FSelector package, we use the correlation coefficient as a unit of valuation. 
# This would be one of the several algorithms contained 
# in the FSelector package that can be used rank the variables.

```{r}
Scores <- linear.correlation(Total~., data_num)
Scores

```
# Getting the top 5 most representative variables
```{r}
Subset <- cutoff.k(Scores, 5)
as.data.frame(Subset)
```

# Getting the best variables
```{r}
Subset1 <-cutoff.k.percent(Scores, 0.4)
as.data.frame(Subset1)
```

```{r}
Subset1 <-cutoff.k.percent(Scores, 0.6)
as.data.frame(Subset1)
```

```{r}
Subset1 <-cutoff.k.percent(Scores, 0.8)
as.data.frame(Subset1)
```

The most important features in descending order are 'Tax', 'cogs', 'gross.income', 'Quantity', 'Unit.price', 'Rating'